quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-17 paper-quollr.Rmd
Add hex coord generation from scratch

- basic example

@@

```{r}
num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", cell_area = 1)
num_bins_x
```

shape_val <- calculate_effective_shape_value(.data = s_curve_noise_umap, x = "UMAP1", y = "UMAP2")
shape_val
```

```{r}
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, x = "UMAP1", y = "UMAP2", shape_val = 1.833091, num_bins_x = num_bins_x)
num_bins_y
```

@@

```{r}
cell_area <- 1
cell_diameter <- sqrt(2 * cell_area / sqrt(3))

hex_size <- cell_diameter/2

@@

```{r}
hex_grid <- gen_hex_coordinates(all_centroids_df)
glimpse(hex_grid)
```

@@

@@

@@

```{r}
num_bins_x <- calculate_effective_x_bins(.data = tSNE_data, x = "tSNE1", cell_area = 1)
num_bins_x <- 13
```

```{r}
shape_val <- calculate_effective_shape_value(.data = tSNE_data, x = "tSNE1", y = "tSNE2")
shape_val
```

```{r}
num_bins_y <- calculate_effective_y_bins(.data = tSNE_data, x = "tSNE1", y = "tSNE2", shape_val = shape_val, num_bins_x = num_bins_x)
num_bins_y
```

>>>>

- basic example
<!--
### Appropriate hex size value to have regular hexagons

min_value_x <- min(s_curve_noise_umap$UMAP1)
max_value_x <- max(s_curve_noise_umap$UMAP1)
min_value_y <- min(s_curve_noise_umap$UMAP2)
max_value_y <- max(s_curve_noise_umap$UMAP2)

# Calculate the maximum span along x and y axes
x_span <- max_value_x - min_value_x
y_span <- max_value_y - min_value_y

hex_size <- min(x_span, y_span)/5.5

num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", hex_size = hex_size)
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, y = "UMAP2", hex_size = hex_size)

all_centroids_df <- generate_full_grid_centroids(nldr_df = s_curve_noise_umap, 
                                                 x = "UMAP1", y = "UMAP2", 
                                                 num_bins_x = num_bins_x, 
                                                 num_bins_y = num_bins_y, 
                                                 buffer_size = NA, hex_size = hex_size)
hex_grid <- gen_hex_coordinates(all_centroids_df, hex_size = hex_size)
ggplot(data = hex_grid, aes(x = x, y = y)) + geom_polygon(fill = "white", color = "black", aes(group = id)) +
  geom_point(data = all_centroids_df, aes(x = x, y = y), color = "red")
```
-->

@@

```{r}
num_bins_x <- calculate_effective_x_bins(.data = s_curve_noise_umap, x = "UMAP1", hex_size = NA)
num_bins_x
```

```{r}
num_bins_y <- calculate_effective_y_bins(.data = s_curve_noise_umap, y = "UMAP2", hex_size = NA)
num_bins_y
```

@@

```{r}
cell_area <- 1

hex_size <- sqrt(2 * cell_area / sqrt(3))

@@

```{r}
hex_grid <- gen_hex_coordinates(all_centroids_df, hex_size = NA)
glimpse(hex_grid)
```

@@

```{r}
## As an option first quantile considered as a default
benchmark_to_rm_lwd_hex <- quantile(df_bin_centroids$std_counts)[2] + 0.01

## To identify low density hexagons
df_bin_centroids_low <- df_bin_centroids |>
  dplyr::filter(std_counts <= benchmark_to_rm_lwd_hex)

## To identify low-density hexagons needed to remove by investigating neighbouring mean density
identify_rm_bins <- find_low_density_hexagons(df_bin_centroids_all = df_bin_centroids, num_bins_x = num_bins_x,
                     df_bin_centroids_low = df_bin_centroids_low)
```

@@

All functions have tests written and implemented using the \CRANpkg{testthat} [@testthat] in R.

@@

```{r}
num_bins_x <- calculate_effective_x_bins(.data = tSNE_data, x = "tSNE1", hex_size = NA)
```

```{r}
num_bins_y <- calculate_effective_y_bins(.data = tSNE_data, y = "tSNE2", hex_size = NA)
num_bins_y
```
